\chapter{Preface}

This book has the objective to add more to the story of life, mainly in wat concerns the concept of Species.
This is not a scientific book, it is just an aggregation of scientific statements used to sustain an idea,
this idea is a departure of the standard interpretation of life centered on the Organism, that adds Species
equally or even more important than them, them Organism.

This book isn't targeted to everybody, in fact, it is targeted to a minority, that thinks that Natural Selection
isn't the full story, and thus is also not a denial of Natural Selection, is just an extension of it. This is
the main reason why it's intended to a minority, by excluding those who deny Natural Selection and those
that think that the entire process ob biological selection is reduced to it.

This book isn't intended to cause strong debates, first by just being targeted to a minority that wants a better
explanation on life, and secondly, by accepting the easy denial arguments of the majority as expectable and self
proofing. For instance, the argument that "group selection" has been disproved and thus Species by being a group
makes "species selection" selection disproved too. That minority that whishes to know better will realize that
group and species are at all the same thing.

The premise of this book is in reality quite simple, are the implications of it that aren't simple at all.
The premise is that of the idea that the "origin of life" and the "origin of species" aren't the same thing,
the idea that half way the story of life the beginning of species happened, and that changed radically the
life itself and all the respective mechanism of selection, including Natural Selection.

But what makes this book a minority targeted book the most, is the idea that Organism are puppet like units
where the Species is their puppeteer, and the refusal of this book is proof of the power of that control.


Rui Monteiro
Lisbon, 2026